---
title: "Site Accounts"
---

```{r, echo = FALSE, output = FALSE}
library(tidyverse)
library(mapview)
library(sf)

load("data/patch_sites.RData")
load("data/patch_tracks.RData")

patch_boundary <- read_sf("data/patch_boundary.gpkg")
```

# Eden Estuary

## Out Head

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Out Head", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Out Head", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Out Head", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Out Head", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Out Head", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Out Head"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Balgove Bay (East)

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Balgove Bay (East)", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Balgove Bay (East)", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Balgove Bay (East)", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Balgove Bay (East)", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Balgove Bay (East)", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Balgove Bay (East)"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

# St Andrews Bay

## West Sands

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "West Sands", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "West Sands", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "West Sands", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "West Sands", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "West Sands", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "West Sands"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Aquarium Viewpoint

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Aquarium Viewpoint", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Aquarium Viewpoint", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Aquarium Viewpoint", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Aquarium Viewpoint", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Aquarium Viewpoint", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Aquarium Viewpoint"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## The Scores

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "The Scores", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "The Scores", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "The Scores", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "The Scores", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "The Scores", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "The Scores"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## East Sands

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "East Sands", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "East Sands", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "East Sands", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "East Sands", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "East Sands", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "East Sands"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Coastal Path from St Andrews

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Coastal Path from St Andrews", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Coastal Path from St Andrews", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Coastal Path from St Andrews", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Coastal Path from St Andrews", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Coastal Path from St Andrews", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Coastal Path from St Andrews"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Maiden Rock

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Maiden Rock", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Maiden Rock", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Maiden Rock", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Maiden Rock", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Maiden Rock", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Maiden Rock"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Sweet Zephyr Overlook

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Sweet Zephyr Overlook", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Sweet Zephyr Overlook", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Sweet Zephyr Overlook", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Sweet Zephyr Overlook", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Sweet Zephyr Overlook", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Sweet Zephyr Overlook"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

# North of Town

## North Haugh Pond

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "North Haugh Pond", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "North Haugh Pond", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "North Haugh Pond", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "North Haugh Pond", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "North Haugh Pond", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "North Haugh Pond"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## North Haugh Meadow 

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "North Haugh Meadow", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "North Haugh Meadow", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "North Haugh Meadow", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "North Haugh Meadow", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "North Haugh Meadow", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "North Haugh Meadow"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## St Andrews Links 

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "St Andrews Links", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "St Andrews Links", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "St Andrews Links", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "St Andrews Links", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "St Andrews Links", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "St Andrews Links"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Balgove Farm 

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Balgove Farm", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Balgove Farm", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Balgove Farm", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Balgove Farm", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Balgove Farm", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Balgove Farm"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Old Course Hotel Bus Stop 

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Old Course Hotel Bus Stop", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Old Course Hotel Bus Stop", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Old Course Hotel Bus Stop", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Old Course Hotel Bus Stop", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Old Course Hotel Bus Stop", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Old Course Hotel Bus Stop"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Swilken Burn to Balgove Bay 

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Swilken Burn to Balgove Bay", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Swilken Burn to Balgove Bay", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Swilken Burn to Balgove Bay", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Swilken Burn to Balgove Bay", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Swilken Burn to Balgove Bay", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Swilken Burn to Balgove Bay"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## David Russell Apartments to Swilken Burn 

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "David Russell Apartments to Swilken Burn", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "David Russell Apartments to Swilken Burn", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "David Russell Apartments to Swilken Burn", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "David Russell Apartments to Swilken Burn", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "David Russell Apartments to Swilken Burn", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "David Russell Apartments to Swilken Burn"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Strathkinness High to Strathkinness Low Roads 

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Strathkinness High to Strathkinness Low Roads", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Strathkinness High to Strathkinness Low Roads", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Strathkinness High to Strathkinness Low Roads", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Strathkinness High to Strathkinness Low Roads", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Strathkinness High to Strathkinness Low Roads", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Strathkinness High to Strathkinness Low Roads"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## B939 (Buchanan Gardens and Strathkinness Low Road) 

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "B939 (Buchanan Gardens and Strathkinness Low Road)", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "B939 (Buchanan Gardens and Strathkinness Low Road)", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "B939 (Buchanan Gardens and Strathkinness Low Road)", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "B939 (Buchanan Gardens and Strathkinness Low Road)", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "B939 (Buchanan Gardens and Strathkinness Low Road)", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "B939 (Buchanan Gardens and Strathkinness Low Road)"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Kinness Burn between Rufflets and Lade Braes

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Kinness Burn between Rufflets and Lade Braes", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Kinness Burn between Rufflets and Lade Braes", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Kinness Burn between Rufflets and Lade Braes", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Kinness Burn between Rufflets and Lade Braes", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Kinness Burn between Rufflets and Lade Braes", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Kinness Burn between Rufflets and Lade Braes"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

# Around Town

## Market Street

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Market Street", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Market Street", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Market Street", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Market Street", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Market Street", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Market Street"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## St Andrews Bus Station

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "St Andrews Bus Station", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "St Andrews Bus Station", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "St Andrews Bus Station", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "St Andrews Bus Station", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "St Andrews Bus Station", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "St Andrews Bus Station"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## St Mary's Quad

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "St Mary's Quad", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "St Mary's Quad", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "St Mary's Quad", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "St Mary's Quad", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "St Mary's Quad", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "St Mary's Quad"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## St Leonard's School

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "St Leonard's School", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "St Leonard's School", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "St Leonard's School", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "St Leonard's School", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "St Leonard's School", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "St Leonard's School"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Doubledykes Road

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Doubledykes Road", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Doubledykes Road", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Doubledykes Road", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Doubledykes Road", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Doubledykes Road", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Doubledykes Road"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Hepburn Gardens

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Hepburn Gardens", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Hepburn Gardens", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Hepburn Gardens", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Hepburn Gardens", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Hepburn Gardens", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Hepburn Gardens"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Kennedy Gardens

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Kennedy Gardens", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Kennedy Gardens", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Kennedy Gardens", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Kennedy Gardens", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Kennedy Gardens", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Kennedy Gardens"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Saint Leonard's Road

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Saint Leonard's Road", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Saint Leonard's Road", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Saint Leonard's Road", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Saint Leonard's Road", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Saint Leonard's Road", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Saint Leonard's Road"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Saint Leonard's Cottage

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Saint Leonard's Cottage", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Saint Leonard's Cottage", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Saint Leonard's Cottage", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Saint Leonard's Cottage", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Saint Leonard's Cottage", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Saint Leonard's Cottage"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## University Hall

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "University Hall", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "University Hall", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "University Hall", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "University Hall", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "University Hall", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "University Hall"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## St Andrews Sports Centre

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "St Andrews Sports Centre", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "St Andrews Sports Centre", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "St Andrews Sports Centre", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "St Andrews Sports Centre", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "St Andrews Sports Centre", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "St Andrews Sports Centre"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## St Andrews Observatory

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "St Andrews Observatory", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "St Andrews Observatory", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "St Andrews Observatory", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "St Andrews Observatory", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "St Andrews Observatory", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "St Andrews Observatory"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Lade Braes

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Lade Braes", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Lade Braes", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Lade Braes", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Lade Braes", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Lade Braes", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Lade Braes"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## St Andrews Botanic Gardens

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "St Andrews Botanic Gardens", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "St Andrews Botanic Gardens", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "St Andrews Botanic Gardens", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "St Andrews Botanic Gardens", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "St Andrews Botanic Gardens", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "St Andrews Botanic Gardens"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## John Knox Road

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "John Knox Road", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "John Knox Road", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "John Knox Road", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "John Knox Road", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "John Knox Road", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "John Knox Road"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Bogward Road

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Bogward Road", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Bogward Road", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Bogward Road", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Bogward Road", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Bogward Road", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Bogward Road"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Broomfaulds Avenue

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Broomfaulds Avenue", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Broomfaulds Avenue", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Broomfaulds Avenue", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Broomfaulds Avenue", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Broomfaulds Avenue", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Broomfaulds Avenue"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Watson Avenue

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Watson Avenue", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Watson Avenue", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Watson Avenue", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Watson Avenue", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Watson Avenue", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Watson Avenue"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Scooniehill Road

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Scooniehill Road", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Scooniehill Road", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Scooniehill Road", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Scooniehill Road", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Scooniehill Road", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Scooniehill Road"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Roundhill Road

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Roundhill Road", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Roundhill Road", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Roundhill Road", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Roundhill Road", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Roundhill Road", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Roundhill Road"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Irvine Crescent

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Irvine Crescent", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Irvine Crescent", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Irvine Crescent", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Irvine Crescent", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Irvine Crescent", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Irvine Crescent"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

# South of Town

## St Andrews Holiday Park

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "St Andrews Holiday Park", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "St Andrews Holiday Park", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "St Andrews Holiday Park", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "St Andrews Holiday Park", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "St Andrews Holiday Park", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "St Andrews Holiday Park"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## A917 between Lamond Drive and B9131

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "A917 between Lamond Drive and B9131", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "A917 between Lamond Drive and B9131", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "A917 between Lamond Drive and B9131", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "A917 between Lamond Drive and B9131", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "A917 between Lamond Drive and B9131", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "A917 between Lamond Drive and B9131"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Farms between A917 and Grange Rd

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Farms between A917 and Grange Rd", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Farms between A917 and Grange Rd", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Farms between A917 and Grange Rd", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Farms between A917 and Grange Rd", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Farms between A917 and Grange Rd", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Farms between A917 and Grange Rd"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Grange Rd Secret Garden

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Grange Rd Secret Garden", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Grange Rd Secret Garden", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Grange Rd Secret Garden", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Grange Rd Secret Garden", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Grange Rd Secret Garden", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Grange Rd Secret Garden"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Farms between A917 and A915

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Farms between A917 and A915", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Farms between A917 and A915", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Farms between A917 and A915", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Farms between A917 and A915", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Farms between A917 and A915", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Farms between A917 and A915"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Fields behind Morrisons & Medical Centre

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Fields behind Morrisons & Medical Centre", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Fields behind Morrisons & Medical Centre", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Fields behind Morrisons & Medical Centre", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Fields behind Morrisons & Medical Centre", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Fields behind Morrisons & Medical Centre", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Fields behind Morrisons & Medical Centre"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Cairnsmill Caravan Park

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Cairnsmill Caravan Park", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Cairnsmill Caravan Park", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Cairnsmill Caravan Park", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Cairnsmill Caravan Park", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Cairnsmill Caravan Park", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Cairnsmill Caravan Park"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Balone Steading

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Balone Steading", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Balone Steading", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Balone Steading", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Balone Steading", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Balone Steading", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Balone Steading"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::

## Lumbo Den

:::::: columns
::: {.column width="47.5%"}

**`{r} patch_sites[patch_sites$locality == "Lumbo Den", "n_species"]`** species observed across **`{r} patch_sites[patch_sites$locality == "Lumbo Den", "n_checklists"]`** checklists in **`{r} patch_sites[patch_sites$locality == "Lumbo Den", "n_months"]`** months. **`{r} round(patch_sites[patch_sites$locality == "Lumbo Den", "sum_duration"])`** total hours of effort covering **`{r} round(patch_sites[patch_sites$locality == "Lumbo Den", "sum_distance"])`** km.

Text.

:::

::: {.column width="5%"}
:::

::: {.column width="47.5%"}
```{r, echo = FALSE, fig.height = 5.1}
mapview(filter(patch_tracks, locality == "Lumbo Den"),
        alpha.regions = 0, legend = FALSE, homebutton = FALSE, layer.name = "Tracks",
        color = "black", popup = FALSE, label = FALSE)
```
:::
::::::
